Circumnuclear Media and Accretion Rates of Quiescent Supermassive Black Holes

### 2015-04-07 ms.tex
caption...
figure

We fix $\beta = 2$ (a typical value) because our results are generally
not sensitive to the properties of the gas flow on radial scales
$\gtrsim r_b$. The presence of the break radius $r_{b}$ is, however,
necessary to obtain a converged steady state for some regions of our
parameter space.  We consider solutions calculated for up to four
values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by the
range of break radii from the \citet{LauerFaber+:2007a}
sample.\footnote{For the core galaxies the break radius follows the
  scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with
  scatter of approximately one dex.  Most the cusp galaxies have $\rb$
  between 100 and 1000 pc, without a clear trend with $\Mbh$.}  In
practice we calculate solutions for a range of $\rb$ only in cases
when its precise value is expected to have a significant affect on the
solution, in particular for high SMBH masses and low heating rates,
for which the stagnation radius approaches large radii. We also
neglect value of $r_b$ which would give unphysically large bulges for
a given $\Mbh$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm edd}$ versus SMBH mass for galaxies in our sample, calculated for different values of the wind heating parameter $\vwO =$ 300 km s$^{-1}$ ({\it green}),
    600 km s$^{-1}$ ({\it orange}), and 1200 km s$^{-1}$ ({\it blue}).
    Squares correspond to cusp galaxies ($\Gamma=0.8$), while
    triangles correspond to cores ($\Gamma$=0.1). Solid and dashed curves correspond to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$ (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies, respectively. }
\end{figure}

>>>>

We fix $\beta = 2$ (a typical value ${\bf AG beta=1.5 may be more
  typical...but it still may not matter...}$) because our results are
generally not sensitive to the properties of the gas flow on radial
scales $\gtrsim r_b$. The presence of the break radius $r_{b}$ is,
however, necessary to obtain a converged steady state for some regions
of our parameter space.  We consider solutions calculated for up to
four values of $\rb$: 50 pc, 100 pc, 200 pc, and 400 pc, motivated by
the range of break radii from the \citet{LauerFaber+:2007a}
sample.\footnote{For the core galaxies the break radius follows the
  scaling relationship $\rb\sim 106 \, (\Mbheight)^{0.39}$ pc, with
  scatter of approximately one dex.  Most the cusp galaxies have $\rb$
  between 100 and 1000 pc, without a clear trend with $\Mbh$.}  In
practice we calculate solutions for a range of $\rb$ only in cases
when its precise value is expected to have a significant affect on the
solution, in particular for high SMBH masses and low heating rates,
for which the stagnation radius approaches large radii. We also
neglect value of $r_b$ which would give unphysically large bulges for
a given $\Mbh$.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{mdot_mass.eps}
  \caption{\label{fig:mdot_mass} Accretion rate $\dot{M}/\dot{M}_{\rm
      edd}$ versus SMBH mass for galaxies in our sample, calculated
    for different values of the wind heating parameter $\vwO =$ 300 km
    s$^{-1}$ ({\it green}), 600 km s$^{-1}$ ({\it orange}), and 1200
    km s$^{-1}$ ({\it blue}).  Squares correspond to cusp galaxies
    ($\Gamma=0.8$), while triangles correspond to cores
    ($\Gamma$=0.1). Green crosses correspond to cusp solutions which
    would be thermally unstable.  Solid and dashed curves correspond
    to our analytic estimates of $\dot{M}/\dot{M}_{\rm edd}$
    (eq.~[\ref{eq:eddr_analytic}]) for cusp and core galaxies,
    respectively. }
\end{figure}
